Paper_stuff

### 2023-10-12 Paper_stuff.Rmd
RCI treatment response figures.

              #deprssion values Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)"
        BL_Dep_level = as.factor(ifelse(BL_CUDOS > 10 & BL_CUDOS <= 20, "Minimal",
                                 ifelse(BL_CUDOS > 20 & BL_CUDOS <= 30, "Mild",
                                 ifelse(BL_CUDOS > 10 & BL_CUDOS <= 45, "Moderate",
                                 ifelse(BL_CUDOS > 45, "Severe",
                                 ifelse(is.na(BL_CUDOS), NA, "Remission"
                                )))))),
        BL_Anx_level = as.factor(ifelse(BL_CUXOS > 10 & BL_CUXOS <= 20, "Minimal",
                                 ifelse(BL_CUXOS > 20 & BL_CUXOS <= 30, "Mild",
                                 ifelse(BL_CUXOS > 10 & BL_CUXOS <= 45, "Moderate",
                                 ifelse(BL_CUXOS > 45, "Severe",
                                 ifelse(is.na(BL_CUXOS), NA, "Remission"
                                )))))),
        Post_Dep_level = as.factor(ifelse(CUDOS_post > 10 & CUDOS_post <= 20, "Minimal",
                                 ifelse(CUDOS_post > 20 & CUDOS_post <= 30, "Mild",
                                 ifelse(CUDOS_post > 10 & CUDOS_post <= 45, "Moderate",
                                 ifelse(CUDOS_post > 45, "Severe",
                                 ifelse(is.na(CUDOS_post), NA, "Remission"
                                )))))),
        Post_Anx_level = as.factor(ifelse(CUXOS_post > 10 & CUXOS_post <= 20, "Minimal",
                                 ifelse(CUXOS_post > 20 & CUXOS_post <= 30, "Mild",
                                 ifelse(CUXOS_post > 10 & CUXOS_post <= 45, "Moderate",
                                 ifelse(CUXOS_post > 45, "Severe",
                                 ifelse(is.na(CUXOS_post), NA, "Remission"
                                )))))))

#7. create new DF with Varaibles we want

AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
                                  Mothership_post$Disorder_treat,
                                  Mothership_post$BL_CUDOS,
                                  Mothership_post$BL_CUXOS,
                                  Mothership_post$CUDOS_pre,
                                  Mothership_post$CUDOS_post,
                                  Mothership_post$CUXOS_pre,
                                  Mothership_post$CUXOS_post,
                                  #Extra stuff?
                                  Mothership_post$BL_Missing,
                                  Mothership_post$Sig_BL,
                                  Mothership_post$Sig_Post,
                                  Mothership_post$Sig_unresponse,
                                  Mothership_post$Sig_unresponse_type
                                  )) #%>%
  #filter(!is.na(Mothership_post$Disorder_treat))

colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "BL_CUDOS", "BL_CUXOS", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post","BL_Missing",
                             "Sig_BL", "Sig_Post","Sig_unresponse", "Sig_unresponse_type")

@@

view(data.frame(table1::table1(~BL_CUXOS + BL_CUDOS + SUManx_DC + SUMdep_DC + CUDOS_post +CUXOS_post, data = Mothership_post)))

@@

@@

AnxDep_response_mean<-AnxDep_PrePost_Long %>%
  filter(!is.na(Sig_unresponse)) |>
  group_by(Test,Sig_unresponse,PrePost) %>%
  summarise(Score=mean(Score,na.rm=TRUE))

ggplot(data=AnxDep_response_mean,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
           group=Test,color=fct_rev(Test)))+
  geom_point(size=2.5) +
  geom_line(group=AnxDep_response_mean$PrePost,size=1.5)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="CUDOS/CUXOS Score")+
  ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank()) +
  facet_wrap(~Sig_unresponse,labeller = labeller(Sig_unresponse =
      c("1" = "Non-responders", 
        "2" = "Responders")
      ))
```

@@

p <- ggplot(data=AnxDep_Treat_mean,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
           group=Test,color=fct_rev(Test)))+
  geom_point(size=2.5) +
  geom_line(group=AnxDep_Treat_mean$PrePost,size=1.5)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="CUDOS/CUXOS Score")+
  labs(
    title = "Mean Pre and Post Scores of the Anxiety and Depression",
    subtitle = "Treatment response based upon Disorder")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank()) +
  facet_grid(Sig_unresponse~Disorder_Type,
             labeller = labeller(
               Sig_unresponse = c("1" = "Non-responders", "2" = "Responders"),
               Disorder_Type = c("1" = "Anxiety", "2" = "BPD", "3" = "Mood", "4" ="Other", "5" = "Trauma")
      ))

#Anxiety     BPD    Mood   Other  Trauma
```

```{r}
Mothership_post <- Mothership_post |>
  #1. Filter out scores for people not in the program / don't have dataa
  filter(!is.na(Days_complete_1)) |>
    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!is.na(CUXOS_pre),
         !is.na(CUXOS_post),
         CUXOS_pre > 0,
         CUXOS_post >= 0,
         !is.na(CUDOS_pre),
         !is.na(CUDOS_post),
         CUDOS_pre > 0,
         CUDOS_post> 0
         ) |>
  mutate(
    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    Anx_Responder = as.factor(
      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50 | CUXOS_post < 20, "Anx Responder",
      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & CUXOS_post < 20,  "Unresponders", "Low BL Anx"      
      )))),
    Dep_Responder = as.factor(
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse", 
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50,  "Unresponders", "Low BL Dep" 
      )))),
    Treatment_Responder = as.factor(
      ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
      ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      )))))))))))

 CUXOS_post == !(CUXOS_post %in% c(seq(1,9,1)))

```{r}
devtools::install_github("AWKruijt/JT-RCI")
library(JTRCI)

# generate some random data:
df <- cbind.data.frame("ppid" = seq(1:64), 
                       "pre" = rnorm(64, 65, 8), 
                       "post" = c(rnorm(32, 40, 8), rnorm(32, 45, 8)),
                       "group" = rep(c("treatment", "control"), each = 32))

# The function will determine which criterion to use based on the available information 
# f.i. when no (healthy or dysfunctional) norm values are provided, the function will  
# return criterion A using the baseline distribution as the 'dysfunctional distribution':

JTRCI(data = df, 
      ppid = "ppid", 
      pre = "pre", 
      post = "post",  
      reliability = .8, 
      indextype = "JT", 
      JTcrit = "auto")

JTRCI (data = RCI_df_anx, 
       pre = "pre", 
       post = "post", 
       ppid = "ID1", 
       reliability = .9, 
       indextype = "JT", 
       JTcrit = 20,
       group = "Disorder",
       facetplot = T,
       plottitle = "Anxeity: JT indices by disorder")

JTRCI(data = df, pre = "pre", post = "post",  group = "group", ppid = "ppid",
      reliability = .8, indextype = "JT", JTcrit = "C",
       normM = 30, normSD = 5, dysfM = 60, dysfSD = 5, 
      facetplot = T, plottitle = "JT indices by group:")
```

# Results
### The overall breakdown of patients’ demographics and diagnoses.
###	The trajectories of depression and anxiety for all patients (both numerical – pre/post scores, overall slope, and visual – graphs). Numerical results are in text, visual results presented to supplement.
- Broken down by treatment duration, treatment track, most common primary diagnoses.
###	The pre-post scores (numerical and visual) for RDQ subscales.
###	Reasons for discharge (numerical and visual).

# Visualizations
### Table – Demographics
### Table – Diagnoses
```{r}
#Demographics Table
Demo_tab_df <- Mothership_Diag_treat |>
  filter(!is.na(Education_1),
         !is.na(Race_1),
         !is.na(Gender_1),
         !is.na(Disorder_Type),
         !is.na(Relationship_1),

```
### Visualization – most common diagnoses.
```{r}
#frequency

@@

>>>>

              #deprssion values Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)"
        BL_Dep_level = as.factor(ifelse(BL_CUDOS > 10 & BL_CUDOS <= 20, "Minimal",
                                 ifelse(BL_CUDOS > 20 & BL_CUDOS <= 30, "Mild",
                                 ifelse(BL_CUDOS > 10 & BL_CUDOS <= 45, "Moderate",
                                 ifelse(BL_CUDOS > 45, "Severe",
                                 ifelse(is.na(BL_CUDOS), NA, "Remission"
                                )))))),
        BL_Anx_level = as.factor(ifelse(BL_CUXOS > 10 & BL_CUXOS <= 20, "Minimal",
                                 ifelse(BL_CUXOS > 20 & BL_CUXOS <= 30, "Mild",
                                 ifelse(BL_CUXOS > 10 & BL_CUXOS <= 45, "Moderate",
                                 ifelse(BL_CUXOS > 45, "Severe",
                                 ifelse(is.na(BL_CUXOS), NA, "Remission"
                                )))))),
        Post_Dep_level = as.factor(ifelse(CUDOS_post > 10 & CUDOS_post <= 20, "Minimal",
                                 ifelse(CUDOS_post > 20 & CUDOS_post <= 30, "Mild",
                                 ifelse(CUDOS_post > 10 & CUDOS_post <= 45, "Moderate",
                                 ifelse(CUDOS_post > 45, "Severe",
                                 ifelse(is.na(CUDOS_post), NA, "Remission"
                                )))))),
        Post_Anx_level = as.factor(ifelse(CUXOS_post > 10 & CUXOS_post <= 20, "Minimal",
                                 ifelse(CUXOS_post > 20 & CUXOS_post <= 30, "Mild",
                                 ifelse(CUXOS_post > 10 & CUXOS_post <= 45, "Moderate",
                                 ifelse(CUXOS_post > 45, "Severe",
                                 ifelse(is.na(CUXOS_post), NA, "Remission"
                                )))))))
    ```
    ```{r}
#devtools::install_github("AWKruijt/JT-RCI")

library(JTRCI)

#devtools::install_github("zieglema/ClinicalSig")
library(ClinicalSig)
# generate some random data:

# https://awkruijt.netlify.app/plotposts/longitudinaljtrci

RCI_df_anx1<-RCI_df_anx |>
  select(ID1,pre,post)

DEP_RCI <- JTRCI (data = RCI_df_dep, 
       pre = "pre", 
       post = "post", 
       ppid = "ID1", 
       reliability = .74, 
       indextype = "RCI", 
       #JTcrit = "auto",
       plottitle = "Anxeity: JT indices by disorder")

ANX_RCI <- JTRCI (data = RCI_df_anx, 
       pre = "pre", 
       post = "post", 
       ppid = "ID1", 
       reliability = .74, 
       indextype = "RCI", 
       #JTcrit = "auto",
       plottitle = "Anxeity: JT indices by disorder")

RCI_DF<- ANX_RCI$data
colnames(RCI_DF) <- paste0(colnames(RCI_DF),"_anx")

RCI_DF2<- DEP_RCI$data
colnames(RCI_DF2) <- paste0(colnames(RCI_DF2),"_dep")

RCI_DF <- full_join(RCI_DF,RCI_DF2, by = c("ppid_anx" = "ppid_dep"))
colnames(RCI_DF)[1] = "ID1"

RCI_DF
```

    ```{r}
Mothership_post <- Mothership_post |>
  #1. Filter out scores for people not in the program / don't have dataa
  filter(!is.na(Days_complete_1)) |>
    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!is.na(CUXOS_pre),
         !is.na(CUXOS_post),
         CUXOS_pre > 0,
         CUXOS_post >= 0,
         !is.na(CUDOS_pre),
         !is.na(CUDOS_post),
         CUDOS_pre > 0,
         CUDOS_post> 0
         ) |>
  mutate(
    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    Anx_Responder = as.factor(
      ifelse(CUXOS_pre < 20 & Percent_Anx_change  <= -50, "Responder",
      ifelse(CUXOS_pre < 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
      )),
    Dep_Responder = as.factor(
      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange <= -50, "Responder",
      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
      )),
    Treatment_Responder = as.factor(
      ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
      ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      )))))))))))

Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1)) |>
  mutate(
    Depression_Responder = ifelse(!is.na(class_RCI_dep), class_RCI_dep, NA),
      Depression_Responder = as.factor(recode(Depression_Responder,
         "1" = "2",
         "2" = "2",
         "3" = "1"
      )),
    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
         Depression_Responder = as.factor(recode(Depression_Responder,
          "2" = "Non-Responder",
          "1" = "Responder"
      )),
    Anxiety_Responder = ifelse(!is.na(class_RCI_anx), class_RCI_anx, NA),
      Anxiety_Responder = as.factor(recode(Anxiety_Responder,
         "1" = "2",
         "2" = "2",
         "3" = "1"
      )),
    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
         Anxiety_Responder = as.factor(recode(Anxiety_Responder,
          "2" = "Non-Responder",
          "1" = "Responder"
      )),
    RESPONDER_FIGS = as.factor(
        ifelse(Anxiety_Responder == "Responder" | Depression_Responder == "Responder", "Responder",
        ifelse(Anxiety_Responder == "Non-Responder" & Depression_Responder == "Non-Responder", "Non-Responder", NA)
        )))

# View(Mothership_joined)
```

    ```{r}
#7. create new DF with Varaibles we want

AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
                                  Mothership_post$Disorder_treat,
                                  Mothership_post$BL_CUDOS,
                                  Mothership_post$BL_CUXOS,
                                  Mothership_post$CUDOS_pre,
                                  Mothership_post$CUDOS_post,
                                  Mothership_post$CUXOS_pre,
                                  Mothership_post$CUXOS_post,
                                  #Extra stuff?
                                  Mothership_post$Depression_Responder,
                                  Mothership_post$Anxiety_Responder,
                                  Mothership_post$RESPONDER_FIGS
                                  )) #%>%
  #filter(!is.na(Mothership_post$Disorder_treat))

colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "BL_CUDOS", "BL_CUXOS", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post","Depression_Responder",
                             "Anxiety_Responder", "RESPONDER_FIGS")

@@

#table1::table1(~BL_CUXOS + BL_CUDOS + SUManx_DC + SUMdep_DC + CUDOS_post +CUXOS_post, data = Mothership_post)

@@

ggplot(data=Pre_DEP,
       aes(x=Disorder_Type,y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_segment(aes(x=Disorder_Type, xend=Post_DEP$Disorder_Type, y=Score, yend=Post_DEP$Score),color = "#4068a8",
              size = 4, #Note that I sized the segment to fit the points
              alpha = .5) +
  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
  geom_point( aes(x=Post_DEP$Disorder_Type, y=Post_DEP$Score), color= "#0CC541", size=3.5) +
  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
       subtitle = "Self Report anxiety was assessed using the CUDOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)",
       ylab = "Disorder Type")+
  scale_y_reverse(limits = c(45,15)) +
  coord_flip() +
  theme_classic()+

  theme(#legend.position = "none",
         plot.background = element_rect(
      fill = "white",
      colour = "white"))
```

```{r}
Mothership_post <- Mothership_post |>
  #1. Filter out scores for people not in the program / don't have dataa
  filter(!is.na(Days_complete_1)) |>
    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!is.na(CUXOS_pre),
         !is.na(CUXOS_post),
         CUXOS_pre > 0,
         CUXOS_post >= 0,
         !is.na(CUDOS_pre),
         !is.na(CUDOS_post),
         CUDOS_pre > 0,
         CUDOS_post> 0
         ) |>
  mutate(
    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    Anx_Responder = as.factor(
      ifelse(CUXOS_pre < 20 & Percent_Anx_change  <= -50, "Responder",
      ifelse(CUXOS_pre < 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
      )),
    Dep_Responder = as.factor(
      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange <= -50, "Responder",
      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
      )),
    Treatment_Responder = as.factor(
      ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
      ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      )))))))))))

 #CUXOS_post == !(CUXOS_post %in% c(seq(1,9,1)))

# Results
### The overall breakdown of patients’ demographics and diagnoses. 
Table – Demographics
Table – Diagnoses
```{r}
#Demographics Table
Demo_tab_df <- Mothership_Diag_treat |>
  filter(!is.na(Education_1),
         !is.na(Race_1),
         !is.na(Gender_1),
         !is.na(Disorder_Type),
         !is.na(Relationship_1)
        )

###	The trajectories of depression and anxiety for all patients (both numerical – pre/post scores, overall slope, and visual – graphs). Numerical results are in text, visual results presented to supplement.

Dumbell Plot by Disorder
```{r}
AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
                                  Mothership_post$Disorder_Type,
                                  Mothership_post$pre_anx,
                                  Mothership_post$post_anx,
                                  Mothership_post$pre_dep,
                                  Mothership_post$post_dep)) 
  # filter(!is.na(Mothership_post$Disorder_Type))
colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post")

Pre_ANX<-ANX_PrePost_mean %>%
  filter(PrePost == "Pre")

ggplot(data=Pre_ANX,
       aes(x=Disorder_Type,y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_segment(aes(x=Disorder_Type, xend=Post_ANX$Disorder_Type, y=Score, yend=Post_ANX$Score),color = "#ad3e4f",
              size = 4, #Note that I sized the segment to fit the points
              alpha = .5) +
  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
  geom_point( aes(x=Post_ANX$Disorder_Type, y=Post_ANX$Score), color= "#0CC541", size=3.5) +
  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
       subtitle = "Self Report anxiety was assessed using the CUXOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
  scale_y_reverse(limits = c(45,15)) +
  coord_flip() +
  theme_classic()+
  facet_wrap(~RESPONDER_FIGS,labeller = labeller(RESPONDER_FIGS =
      c("1" = "Non-Responders", 
        "2" = "Responders")
  ))
  theme(#legend.position = "none",
         plot.background = element_rect(
      fill = "white",
      colour = "white"))

@@

AnxDep_response_mean<-AnxDep_PrePost_Long %>%
  filter(!is.na(RESPONDER_FIGS)) |>
  group_by(Test,RESPONDER_FIGS,PrePost) %>%
  summarise(Score=mean(Score,na.rm=TRUE))

ggplot(data=AnxDep_response_mean,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
           group=Test,color=fct_rev(Test)))+
  geom_point(size=2.5) +
  geom_line(group=AnxDep_response_mean$PrePost,size=1.5)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="CUDOS/CUXOS Score")+
  ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank()) +
  facet_wrap(~RESPONDER_FIGS,labeller = labeller(RESPONDER_FIGS =
      c("1" = "Non-Responders", 
        "2" = "Responders")
      ))
```

@@

p <- ggplot(data=AnxDep_Treat_mean,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
           group=Test,color=fct_rev(Test)))+
  geom_point(size=2.5) +
  geom_line(group=AnxDep_Treat_mean$PrePost,size=1.5)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="CUDOS/CUXOS Score")+
  labs(
    title = "Mean Pre and Post Scores of the Anxiety and Depression",
    subtitle = "Treatment response based upon Disorder")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank()) +
  facet_grid(Sig_unresponse~Disorder_Type,
             labeller = labeller(
               Sig_unresponse = c("1" = "Non-responders", "2" = "Responders"),
               Disorder_Type = c("1" = "Anxiety", "2" = "BPD", "3" = "Mood", "4" ="Other", "5" = "Trauma")
      ))
p 
#Anxiety     BPD    Mood   Other  Trauma
```

- Broken down by treatment duration, treatment track, most common primary diagnoses.
###	The pre-post scores (numerical and visual) for RDQ subscales.
###	Reasons for discharge (numerical and visual).

# Visualizations

### Visualization – most common diagnoses.
```{r}
#frequency

@@

```{r}
Mothership_Long_anx <- gather(Mothership,rm,CUXOS,Day1_CUXOS:Day40_CUXOS,factor_key = "T")
Mothership_Long_anx <- Mothership_Long_anx[order(Mothership_Long_anx$ID1),]

#Create a Time Variable
Mothership_Long_anx$TxDay <- NA
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day1_CUXOS"]<-1
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day2_CUXOS"]<-2
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day3_CUXOS"]<-3
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day4_CUXOS"]<-4
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day5_CUXOS"]<-5
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day6_CUXOS"]<-6
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day7_CUXOS"]<-7
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day8_CUXOS"]<-8
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day9_CUXOS"]<-9
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day10_CUXOS"]<-10
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day11_CUXOS"]<-11
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day12_CUXOS"]<-12
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day13_CUXOS"]<-13
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day14_CUXOS"]<-14
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day15_CUXOS"]<-15
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day16_CUXOS"]<-16
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day17_CUXOS"]<-17
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day18_CUXOS"]<-18
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day19_CUXOS"]<-19
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day20_CUXOS"]<-20

# #Create a New Data Set with an Average Anxiety Variable
# Mothership_Mean_CUXOS<-Mothership_Long_anx %>%
#   group_by(TxDay) %>%
#   summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

#plot Anxiety mean with each group

# New dataset for the treatment duration Anxiety plot
Mothership_Mean_CUXOS<-Mothership_Long_anx %>%
  group_by(Duration,TxDay) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

Mothership_duration_CUXOS<-Mothership_Mean_CUXOS[1:83,]
#delete weird Na values and put NA for values
Mothership_duration_CUXOS[6:20,3] = NA
Mothership_duration_CUXOS[37:41,3] = NA
Mothership_duration_CUXOS[74:83,3] = NA
Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-21),]
Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-41),]
Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-61),]
Mothership_duration_CUXOS

ggplot(data=Mothership_duration_CUXOS,aes(x=TxDay,y=mean_CUXOS,group=Duration,color=Duration))+
  geom_line(size=1)+
  geom_point()+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Anxiety Severity During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Anxiety Severity",limits=c(5,50,by=5))+
  scale_color_manual(values=c("#BB9D00","red",
                              "darkred","orange"))+
  theme(panel.background=NULL)+
  labs(subtitle = "Broken up by Duration of Treatment")
```

```{r}
Mothership_Long_dep <- gather(Mothership,rm,CUDOS,Day1_CUDOS:Day40_CUDOS,factor_key = "T")
Mothership_Long_dep <- Mothership_Long_dep[order(Mothership_Long_dep$ID1),]

Mothership_Long_dep
#Create a Time Variable
Mothership_Long_dep$TxDay <- NA
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day1_CUDOS"]<-1
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day2_CUDOS"]<-2
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day3_CUDOS"]<-3
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day4_CUDOS"]<-4
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day5_CUDOS"]<-5
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day6_CUDOS"]<-6
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day7_CUDOS"]<-7
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day8_CUDOS"]<-8
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day9_CUDOS"]<-9
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day10_CUDOS"]<-10
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day11_CUDOS"]<-11
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day12_CUDOS"]<-12
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day13_CUDOS"]<-13
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day14_CUDOS"]<-14
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day15_CUDOS"]<-15
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day16_CUDOS"]<-16
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day17_CUDOS"]<-17
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day18_CUDOS"]<-18
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day19_CUDOS"]<-19
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day20_CUDOS"]<-20
